---
title: "fars_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fars_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r set_global_options, include=FALSE}
knitr::opts_chunk$set(error = TRUE)
```

# Package Description

This package analyzes data from the US National Highway Traffic Safety Administration's Fatality Analysis Reporting System, which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes. Users can read a csv, subset data by month/year, summarise accident occurrence for specific time and visualize the result US map by state.


```{r import libraries}
library(Fars)
library(dplyr)
library(maps)
```

## Data included in the package

```{r}
list.files(system.file("extdata", package = "Fars"))
```


## Summary of package functions

### Function `make_filename`

This function makes a file name for the chosen year:

```{r}
yr <- 2015
make_filename(yr)
```

### Function `fars_read_years`

This simple function subsets month and year from the file for the chosen year.

```{r}
fars_read_years(2013)
```


### Function `fars_summarize_years`

This simple function summarises the accident events by month and year in a chosen year(s)

```{r}
plot(fars_summarize_years(2015))
fars_summarize_years(c(2015, 2014))
```

### Function `fars_map_state`

The function displays accident events on the US map for a chosen state and year.

```{r}
state_num <- 49 # Utah
yr <- 2014
fars_map_state(state_num, yr)
```

